```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,fig.width = 8,fig.height = 8)
```

## Top dogs

In this homework, you will try to reproduce the fantastic infographic for [top dogs](https://informationisbeautiful.net/visualizations/best-in-show-whats-the-top-data-dog/), originally produced by David McCandless. The raw data can be found [here](https://docs.google.com/spreadsheets/d/1l_HfF5EaN-QgnLc2UYdCc7L2CVrk0p3VdGB1godOyhk/edit#gid=10). You can download this file by File -- Download As -- Microsoft Excel (.xlsx).

**Submission instructions**: Create a folder named `ds202_hw6`, and name the RMarkDown file including your solutions `hw6.Rmd` under this folder. For the submission, create a GitHub repository named `ds202_hw6` under your GitHub account, and push both `hw6.Rmd` and the knitted `hw6.html` before the deadline. I will assume you use the same GitHub username as for your HW5 submission. The latest version of your homework appearing on GitHub before the deadline is graded. *It is crucial to follow the exact folder structure and file names*, so that your homework can be reproduced and graded by an automated script. This homework is **due on April 22** before class.

1. Import the data and clean appropriately. To read in the data, you can use `readxl::read_xlsx('fileNameHere', sheet='sheetNameHere')`. Required data are in the sheets `Best in show` and `Best in show full sheet`. Take extra care on the column names and the first few rows of the data frame after read in.
```{r}
library(dplyr)
library(tidyverse)
library(ggplot2)
best<-readxl::read_xlsx("KIB - Best in Show (public).xlsx",sheet='Best in show')
full<-readxl::read_xlsx("KIB - Best in Show (public).xlsx",sheet='Best in show full sheet')
#extract dog breed, category, datadog score, popularity, intelligence, size
data<-full%>%select(1,3,5,6,11,32)
data<-data[-(1:3),]
names(data)<-c("dog breed","category","score","popularity","intelligence","size")
data<-na.omit(data)
data$category<-as.factor(data$category)
data$size<-as.factor(data$size)
data<- data%>%mutate(score= as.numeric(score), popularity = as.numeric(popularity),intelligence = as.numeric(intelligence))
data <- data %>% mutate(intelligence = ifelse(intelligence<65,"clever","dumb"))
str(data)
```

2. Create a graphics similar to the  [top dogs](https://informationisbeautiful.net/visualizations/best-in-show-whats-the-top-data-dog/) figure. Your figure needs to display the following information with appropriate plotting elements:

- breed of dog
- type of dog (work, toy, etc.)
- size of dog
- data score 
- popularity
- intelligence of the dog
- appropriate legends & explanation

Hints and Notes:

- The breed of dog can be displayed without the silhouttes (text only is fine)
- Avoid (too much) overlaps!
- Choose a good color scheme.
- Your submission is supposed to be fully reproducible, i.e. the TA and I will 'knit' your submission in RStudio. 

```{r}
temp<-data%>%filter(`dog breed`=="Staffordshire Bull Terrier")
score_mid= temp$score - 0.07
popularity_mid=temp$popularity +2

plot<-data%>%ggplot(aes(x=score,y=popularity,color=category,shape=intelligence,size=size))+geom_point(alpha=0.7)+geom_text(aes(label=`dog breed`),size=2.1,vjust = 0, nudge_y = 1.6)+scale_y_reverse() +geom_vline(xintercept = score_mid)+geom_hline(yintercept = popularity_mid)+ggtitle("Best in Show: The Ultimate Data Dog")

plot<-plot+theme(axis.ticks= element_blank(),axis.title = element_blank(),axis.text = element_blank(),panel.background = element_blank())

plot+ annotate("text",x=1.3,y=0,label="Inexplicably Overrated")+ annotate("text",x=score_mid+0.05,y=0,label="popularity")+ annotate("text",x=3.5,y=0,label="Hot Dogs!")+annotate("text",x=1.3,y=160,label="The Rightly Ignored")+annotate("text",x=3.3,y=160,label="Overlooked Treasures")


```
